\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2015-01-08 proposal/sections/implication-risk.tex
add some text to risks.

\subsection*{implications}

@@

>>>>

\subsection*{Implications and challenges}
One of the biggest challenge in the project is the basic research to detect unique brain waves. When our research has success and we are able to detect it, there are many use cases in other topics. One use case could be usage for high secure applications and systems. Where biometrical methods has some disadvantages, we have discussed above, our method can reduce this disadvantages.
Other topics could be the medicine. Current we know only a little bit about brain waves. With our research we could increase our medical understanding of brain waves.

@@

\subsubsection*{Missinterpretion}
\begin{itemize}
 \item Description: The team members not understand the specification correctly.
 \item Solution: Make meetings and reviews to ensure that every team member has understand it correctly.
\end{itemize}
